A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-15 Supplementary_figures.tex
next on \subsection{Research limitation}

\documentclass[preprint,12pt]{elsarticle}

@@

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

@@

% Authors, for the paper (add full first names)
%\Author{
Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
Michael Hsiao $^{3}$*
and Yu-Chuan (Jack) Li $^{1,4}$*%\orcidB{}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

@@

Supplementary Figure S1\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

Supplementary Figure S2\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

Supplementary Figure S3\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
\clearpage

@@

\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
\clearpage

@@

\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{figure:fig_GSE2837}
\end{figure}
\clearpage

>>>>

% Supplementary_figures.tex
\documentclass[preprint,12pt]{elsarticle}

@@

%%% for abbreviations, or acronyms
\usepackage[acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

@@

% Authors, for the paper (add full first names)
%\Author{
Li-Hsing Chi $^{1,2}$%\orcidA{}
, Alexander TH Wu $^{1}$,
Michael Hsiao $^{3}$*
and Yu-Chuan (Jack) Li $^{1,4}$*%\orcidB{}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

@@

Supplementary Figure S\ref{fig:fig_SurvExpress}\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

Supplementary Figure S\ref{fig:fig_HPA_USP10}\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

Supplementary Figure S\ref{fig:fig_GSE2837}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=10cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
\clearpage

@@

\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
\clearpage

@@

\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{fig:fig_GSE2837}
\end{figure}
\clearpage
